HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-01-22 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
Update to Abstract

\abstract{The High Energy Phyiscs community has developed and needs to maintain
many tens of millions of lines of code and to integrate effectively the
work of thousands of developers across large collaborations. 
Software needs to be built, validated, and deployed across hundreds of
sites. Software also has a lifetime of many years, frequently beyond that
of the original developer, it must be developed with sustainability in
mind. Adequate recognition of software development as a critical task in the HEP
community needs to be fostered and an appropriate publication and citation
strategy needs to be developed. As part of the HEP Softare Foundation's
Community White Paper process a working group on Software Development,
Deployment and Validation was formed to examine all of these
issues, identify best practice and to formulare recommendations for the next
decade. Its report is presented here.}

@@

\title{HEP Software Foundation Community White Paper Working Group -- Software
Development, Deployment and Validation}

\author{HEP Software Foundation:}
\author[a]{Benjamin Couturier}
\author[a,1]{Giulio Eulisse}
\author[b]{Hadrien Grasland}
\author[a]{Benedikt Hegner}
\author[b]{Michel Jouvin}
\author[c]{Meghan Kane}
\author[d]{Daniel S. Katz}
\author[e]{Thomas Kuhr}
\author[f]{David Lange}
\author[a,1]{Patricia Mendez Lorenzo}
\author[e]{Martin Ritter}
\author[a,1]{Graeme Andrew Stewart}
\author[a]{Andrea Valassi}

\affiliation[a]{CERN, Geneva, Switzerland}
\affiliation[b]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[c]{Soundcloud, Berlin, Germany}
\affiliation[d]{University of Illinois Urbana-Champaign, Champaign, Illinois,
USA}
\affiliation[e]{Fakultät für Physik, Ludwig-Maximilians-Universität München,
München, Germany}
\affiliation[f]{Princeton University, Princeton, USA}
\affiliation[1]{Paper Editor}

@@

>>>>

\abstract{ A working group on detector simulation was formed as part of the HEP 
Software Foundation's initiative to prepare a Community White Paper that describes 
the main software challenges and opportunities to be faced in our field over the next 
decade. The working group met over a period of several months in order to review the 
current status of the Full and Fast simulation applications of HEP experiments 
and the improvements that will need to be made in order to meet the goals of future HEP 
experimental programmes.  The scope of the topics covered includes the main components 
of a HEP simulation application, including MC truth handling, geometry modeling, particle 
propagation in materials and fields, physics modeling of the interactions of particles 
with matter, the treatment of pileup and other backgrounds, as well as signal processing 
and digitisation. The work programme described in this document focuses on the need to 
improve both software and physics performance, in view of the need to improve statistical precision
and to address the diversification of physics programmes.}

@@

\title{HEP Software Foundation Community White Paper Working Group -- Detector Simulation}

\author{HEP Software Foundation:}
\author[f,1]{Victor D. Elvira}
\author[a,1]{John Harvey}

\affiliation[a]{CERN, Geneva, Switzerland}
\affiliation[b]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[c]{University of Illinois Urbana-Champaign, Champaign, Illinois,
USA}
\affiliation[d]{FNAL, Fermilab, Batavia IL 60510- 5011, USA}
\affiliation[f]{Princeton University, Princeton, USA}
\affiliation[1]{Paper Editor}

@@

\end{document}
